Verifying Demonstrations

### 2017-11-15 contents-poster.tex
Updates colouring of blocks

    \begin{block}{Scenario: The crowd-counting problem}
      \begin{itemize}
        \item Alice organizes a protest against Eve's regime.
        \item Bob, Carol and others show up.
        \item We want to know how many showed up to support Alice.
      \end{itemize}
    \end{block}

    \begin{figure}
      \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
    \end{figure}

    \begin{example}[Current methods]
      \begin{itemize}
        \item Computer vision does object recognition.
        \item Requires photos/video that cover the entire location, all the time.
        \item This will count people twice.
      \end{itemize}
    \end{example}

    \begin{example}[Suggested ideas]
      \begin{itemize}
        \item Scan active mobile phones in the area.
        \item This requires some extra equipment.
        \item This catches bystanders who are not protesting.
      \end{itemize}
    \end{example}

@@

    \begin{requirements}[V]
    \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
      participation proof provides temporal and spatial eligibility and that it 
      has not been counted before.

@@

    \item\label{IndividualVerif} Individual verifiability: every participant can 
      verify that their participation proof is included in the global count.
    \end{requirements}

>>>>

    \begin{blueblock}{Scenario: The crowd-counting problem}
      \begin{itemize}
        \item Alice organizes a protest against Eve's regime.
        \item Bob, Carol and others show up.
        \item We want to know how many showed up to support Alice's cause.
      \end{itemize}
    \end{blueblock}

    \begin{figure}
      \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
      \caption{%
        Mostly used method, Jacob's method: divide the area into regions, 
        estimate the density in each region, sum them up.
      }
    \end{figure}

    \begin{orangeblock}{Computer vision methods}
      \begin{itemize}
        \item Computer vision does object recognition.
        \item Requires photos/video that cover the entire location, all the time.
        \item This will count people twice.
      \end{itemize}
    \end{orangeblock}

    \begin{orangeblock}{Other methods}
      \begin{itemize}
        \item Scan active mobile phones in the area.
        \item This requires some extra equipment.
        \item This catches bystanders who are not protesting.
      \end{itemize}
    \end{orangeblock}

@@

    \begin{blueblock}{Requirements}
      \begin{itemize}
        \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
          participation proof provides temporal and spatial eligibility and that 
          it has not been counted before.

@@

        \item\label{IndividualVerif} Individual verifiability: every participant 
          can verify that their participation proof is included in the global 
          count.
      \end{itemize}
    \end{blueblock}

    \begin{greenblock}{Our approach}
      \dots
    \end{greenblock}
